---
title: "LLM & Human Possibilities, Study 1"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(tibble)
library(readr)
library(ggplot2)
library(ggrepel)
library(lme4)
library(lmerTest)
library(emmeans)
library(knitr)
library(purrr)
library(janitor)
library(stringr)
library(psych)

knitr::opts_chunk$set(echo = TRUE, dpi = 300, fig.width = 7)
```


# Read in Data

Two CSV files were exported from Qualtrics, one per experimental condition
(LLM-generated options; Human-generated options). The first two rows of each
Qualtrics export contain metadata and are removed. Column names are
standardised to snake_case using `clean_names()`. For the LLM file, condition
prefixes are renamed from `c3`/`c4` to `c1`/`c2` to match the Human file
structure.

```{r read-data, echo=FALSE}
main_LLM.df <- read.csv("Main_LLM.csv", check.names = FALSE) %>%
  slice(-c(1:2)) %>%
  clean_names() %>%
  select(-matches("_response")) %>%
  rename_with(~ gsub("^c3_", "c1_", .)) %>%
  rename_with(~ gsub("^c4_", "c2_", .)) %>%
  mutate(experiment = "LLM")

main_Human.df <- read.csv("Main_Human.csv", check.names = FALSE) %>%
  slice(-c(1:2)) %>%
  clean_names() %>%
  select(-matches("_fr_")) %>%
  mutate(experiment = "Human")

# Combine and retain only fully completed responses
main.df <- bind_rows(main_LLM.df, main_Human.df) %>%
  filter(progress == 100)
```


# Participant Exclusions

Participants were excluded if: (1) their reCAPTCHA score indicated bot-like
behaviour (score ≤ 0.5), or (2) they reported a faulty LLM option display via
the post-study feedback question.

```{r exclusions, echo=FALSE}
main.df <- subset(
  main.df,
  !(q_recaptcha_score <= 0.5 |
    grepl("Yes, this happed to me. (Please write down for which scenario if you can recall it).", feedback1, fixed = TRUE) |
    grepl("Yes, this happed to me. (Please write down for which scenario if you can recall it).", feedback2, fixed = TRUE)
  )
)
```


# Demographics

```{r demographics, echo=FALSE}
desc1.df <- main.df %>%
  select(duration_in_seconds, ethnicity, ethnicity_10_text, gender) %>%
  mutate(duration_in_seconds = as.numeric(duration_in_seconds)) %>%
  summarise(
    n             = n(),
    female        = sum(gender == "Female"),
    male          = sum(gender == "Male"),
    non_binary    = sum(gender == "Non-Binary"),
    undisclosed   = sum(gender == "Prefer not to say"),
    other         = sum(gender == "Other"),
    white         = sum(ethnicity == "Caucasian/White"),
    black         = sum(ethnicity == "Black/African"),
    latino        = sum(ethnicity == "Hispanic/Latinx"),
    native        = sum(ethnicity == "Alaskan or American Indian"),
    asian         = sum(ethnicity == "Asian"),
    east          = sum(ethnicity == "Middle Eastern or Northern African"),
    multi         = sum(ethnicity == "Multiethnic"),
    e_undisclosed = sum(ethnicity == "Prefer not to disclose"),
    mean_time     = mean(duration_in_seconds / 60),
    sd_time       = sd(duration_in_seconds / 60)
  )

desc_age.df <- main.df %>%
  mutate(age_1_text = as.numeric(age_1_text)) %>%
  select(age_1_text) %>%
  filter(age_1_text != "", age_1_text < 100) %>%
  summarise(
    mean_age = mean(age_1_text, na.rm = TRUE),
    sd_age   = sd(age_1_text,  na.rm = TRUE)
  )

# Table 1: Gender and ethnicity
gender_ethnicity_table <- data.frame(
  Category = c("Female", "Male", "Non-binary", "Prefer not to say", "Other",
               "Caucasian/White", "Black/African", "Hispanic/Latinx",
               "Alaskan or American Indian", "Asian",
               "Middle Eastern or Northern African", "Multiethnic",
               "Prefer not to disclose"),
  Group = c(rep("Gender", 5), rep("Ethnicity", 8)),
  N = c(desc1.df$female, desc1.df$male, desc1.df$non_binary,
        desc1.df$undisclosed, desc1.df$other,
        desc1.df$white, desc1.df$black, desc1.df$latino,
        desc1.df$native, desc1.df$asian, desc1.df$east,
        desc1.df$multi, desc1.df$e_undisclosed)
)
knitr::kable(gender_ethnicity_table, caption = "Gender and Ethnicity")

# Table 2: Age and study duration
time_age_table <- data.frame(
  Measure = c("Age (years)", "Study duration (minutes)"),
  Mean    = round(c(desc_age.df$mean_age, desc1.df$mean_time), 2),
  SD      = round(c(desc_age.df$sd_age,   desc1.df$sd_time),   2)
)
knitr::kable(time_age_table, caption = "Age and Study Duration")
```


# Data Preparation

## Main Dataframe

The raw data are reshaped from wide to long format and back, parsing each
column name to extract: the experimental condition (`c1` = judgment last,
`c2` = judgment first), the scenario number (1–9), and the response type
(probability, morality, and normality ratings for each of 5 generated options,
the actual action, blame, and counterfactual ratings). Participants who
reported display issues in either feedback question are removed at this stage.

```{r create-exp1, echo=FALSE}
exp1.df <- main.df %>%
  mutate(participant = 1:n()) %>%
  select(c1_s1_t_first_click:c2_s9_cf5_6,
         participant,
         response_id,
         experiment,
         feedback1,
         feedback2) %>%
  select(-contains("last_click"), -contains("click_count")) %>%
  filter(!grepl("^yes", feedback1, ignore.case = TRUE)) %>%
  filter(!grepl("^yes", feedback2, ignore.case = TRUE)) %>%
  select(-feedback1, -feedback2) %>%
  gather(condition, response, -participant, -response_id, -experiment) %>%
  filter(response != "") %>%
  mutate(exp_condition = case_when(
    str_detect(condition, "c1_") ~ "judgment last",
    str_detect(condition, "c2_") ~ "judgment first"
  )) %>%
  mutate(scenario = case_when(
    str_detect(condition, "s1_") ~ "scenario 1",
    str_detect(condition, "s2_") ~ "scenario 2",
    str_detect(condition, "s3_") ~ "scenario 3",
    str_detect(condition, "s4_") ~ "scenario 4",
    str_detect(condition, "s5_") ~ "scenario 5",
    str_detect(condition, "s6_") ~ "scenario 6",
    str_detect(condition, "s7_") ~ "scenario 7",
    str_detect(condition, "s8_") ~ "scenario 8",
    str_detect(condition, "s9_") ~ "scenario 9"
  )) %>%
  mutate(responsetype = case_when(
    str_detect(condition, "a1_4") ~ "prob_resp_1",
    str_detect(condition, "a1_5") ~ "moral_resp_1",
    str_detect(condition, "a1_6") ~ "normal_resp_1",
    str_detect(condition, "a2_4") ~ "prob_resp_2",
    str_detect(condition, "a2_5") ~ "moral_resp_2",
    str_detect(condition, "a2_6") ~ "normal_resp_2",
    str_detect(condition, "a3_4") ~ "prob_resp_3",
    str_detect(condition, "a3_5") ~ "moral_resp_3",
    str_detect(condition, "a3_6") ~ "normal_resp_3",
    str_detect(condition, "a4_4") ~ "prob_resp_4",
    str_detect(condition, "a4_5") ~ "moral_resp_4",
    str_detect(condition, "a4_6") ~ "normal_resp_4",
    str_detect(condition, "a5_4") ~ "prob_resp_5",
    str_detect(condition, "a5_5") ~ "moral_resp_5",
    str_detect(condition, "a5_6") ~ "normal_resp_5",
    str_detect(condition, "ar_4") ~ "prob_resp_act",
    str_detect(condition, "ar_5") ~ "moral_resp_act",
    str_detect(condition, "ar_6") ~ "normal_resp_act",
    str_detect(condition, "b_")   ~ "blame",
    str_detect(condition, "cf1")  ~ "cf_1",
    str_detect(condition, "cf2")  ~ "cf_2",
    str_detect(condition, "cf3")  ~ "cf_3",
    str_detect(condition, "cf4")  ~ "cf_4",
    str_detect(condition, "cf5")  ~ "cf_5",
    str_detect(condition, "first_click") ~ "first_click",
    str_detect(condition, "page_submit") ~ "page_submit"
  )) %>%
  select(-condition) %>%
  pivot_wider(names_from = responsetype, values_from = response)
```

```{r reshape, echo=FALSE}
# Long format: one row per participant × scenario × option × rating dimension
exp1_long.df <- exp1.df %>%
  gather(responsetype, response,
         -scenario, -participant, -response_id, -exp_condition,
         -experiment, -first_click, -page_submit, -blame) %>%
  mutate(response_order = case_when(
    str_detect(responsetype, "_1")   ~ "1",
    str_detect(responsetype, "_2")   ~ "2",
    str_detect(responsetype, "_3")   ~ "3",
    str_detect(responsetype, "_4")   ~ "4",
    str_detect(responsetype, "_5")   ~ "5",
    str_detect(responsetype, "_act") ~ "act"
  )) %>%
  mutate(response_category = case_when(
    str_detect(responsetype, "prob_")   ~ "probability",
    str_detect(responsetype, "moral_")  ~ "morality",
    str_detect(responsetype, "normal_") ~ "normality",
    str_detect(responsetype, "cf_")     ~ "counterfactual"
  )) %>%
  select(-responsetype)

# Wide format including all response orders (generated options + actual action).
# Probability, morality, and normality are averaged into a composite value (avg).
exp1_wide_all.df <- exp1_long.df %>%
  pivot_wider(names_from = response_category, values_from = response) %>%
  mutate(across(c(probability, morality, normality), as.numeric)) %>%
  mutate(avg = (normality + probability + morality) / 3)

# Generated options only (response_order 1–5), long format including avg composite.
# Used for the sample sum calculation.
exp1_long_avg.df <- exp1_wide_all.df %>%
  pivot_longer(
    cols      = c(probability, morality, normality, avg),
    names_to  = "response_category",
    values_to = "response"
  ) %>%
  filter(response_order != "act") %>%
  mutate(response = as.numeric(response))

# Actual action ratings only (response_order = "act"), long format.
# Used to obtain each participant's baseline action value for the sample sum.
exp1_long_act.df <- exp1_wide_all.df %>%
  pivot_longer(
    cols      = c(probability, morality, normality, avg),
    names_to  = "response_category",
    values_to = "response"
  ) %>%
  filter(response_order == "act") %>%
  mutate(response = as.numeric(response))

# Wide format for the actual action only. Used for the actual action value model.
exp1_wide_act.df <- exp1_long.df %>%
  filter(response_order == "act") %>%
  pivot_wider(names_from = response_category, values_from = response) %>%
  mutate(across(c(probability, morality, normality), as.numeric)) %>%
  mutate(avg = (normality + probability + morality) / 3) %>%
  mutate(experiment = relevel(factor(experiment), ref = "Human"))

# Wide format for generated options only (response_order 1–5), with experiment
# releveled and response_order treated as an ordered factor. Used for option value models.
exp1_wide.df <- exp1_long.df %>%
  pivot_wider(names_from = response_category, values_from = response) %>%
  mutate(across(c(probability, morality, normality), as.numeric)) %>%
  mutate(avg = (normality + probability + morality) / 3) %>%
  filter(response_order != "act") %>%
  mutate(
    experiment     = relevel(factor(experiment), ref = "Human"),
    response_order = ordered(as.integer(as.character(response_order)), levels = 1:5)
  )
```


# Analysis

## Internal Consistency of Ratings

The three rating dimensions (probability, morality, normality) were examined
for internal consistency across all generated options.

```{r reliability, message=FALSE, warning=FALSE}
ratings_matrix <- exp1_wide.df %>%
  select(probability, morality, normality) %>%
  filter(complete.cases(.))

alpha_result <- psych::alpha(ratings_matrix)

# Average inter-rating r (mean of pairwise correlations)
cor_matrix <- cor(ratings_matrix, use = "complete.obs")
mean_r <- mean(cor_matrix[upper.tri(cor_matrix)])

# Summary: Cronbach's alpha and average inter-rating r
data.frame(
  measure = c("Cronbach's alpha", "Average inter-rating r"),
  value   = round(c(alpha_result$total$raw_alpha, mean_r), 2)
)

# Corrected rating-composite correlations
round(alpha_result$item.stats[, "r.cor", drop = FALSE], 2)
```


## Sample Sum

For each participant and scenario, we calculate the **sample sum**: the total
amount by which the generated options exceed the value of the agent's actual
action. Formally, for each option whose composite value exceeds the action's
composite value, we sum the difference. Participants missing actual action
ratings across all scenarios are excluded; for the small number of cases where
a single scenario's actual action rating is missing, that scenario is skipped
and the corresponding sample sum entry is left as NA (excluded from the blame
models below).

```{r sample-sum}
# Identify and exclude participants missing ALL actual action ratings
participant_numbers <- exp1_long_act.df %>%
  filter(response_category == "avg") %>%
  group_by(participant) %>%
  summarise(all_missing = all(is.na(response)), .groups = "drop") %>%
  filter(all_missing) %>%
  pull(participant)

withinData <- exp1_long_avg.df %>%
  mutate(sampleSum = NA) %>%
  ungroup() %>%
  filter(!participant %in% participant_numbers)

for (subj in unique(withinData$participant)) {
  d <- withinData %>% filter(participant == subj)

  for (e in unique(d$experiment)) {
    for (c in unique(d$scenario)) {

      # Composite ratings for each generated option
      pgSamp <- exp1_long_avg.df %>%
        filter(participant == subj, scenario == c,
               experiment == e, response_category == "avg") %>%
        pull(response)

      # Composite rating for the actual action
      a_val <- exp1_long_act.df %>%
        filter(participant == subj, scenario == c,
               experiment == e, response_category == "avg") %>%
        pull(response)

      # Skip if actual action rating is missing for this scenario
      if (length(a_val) == 0 || is.na(a_val)) next

      # Sample sum: total excess of generated options over the actual action
      withinData$sampleSum[
        withinData$participant == subj &
        withinData$scenario    == c    &
        withinData$experiment  == e
      ] <- sum(pgSamp[pgSamp > a_val] - a_val)
    }
  }
}

```

```{r create-model-df, echo=FALSE}
# One row per participant × scenario: avg composite rating and blame rating
exp1_model.df <- withinData %>%
  filter(response_order == 1 & response_category == "avg") %>%
  mutate(blame = as.numeric(blame))

# Remove the small number of rows with missing sampleSum (scenario-level
# missingness) so all blame models are fitted on identical data
exp1_blame.df <- exp1_model.df %>%
  filter(!is.na(sampleSum))
```


## Value of Generated Options

We used linear mixed-effects models (LMERs) to examine whether the composite
value of generated options differed between experimental conditions (LLM vs.
Human) and across generation order (options 1–5). Scenario and participant were
included as crossed random intercepts. Models were compared using likelihood
ratio tests (ML estimation).

```{r option-values, message=FALSE, warning=FALSE}
model_0 <- lmer(avg ~ 1 + (1 | scenario) + (1 | participant),
                data = exp1_wide.df, REML = FALSE)

model_1 <- lmer(avg ~ experiment + (1 | scenario) + (1 | participant),
                data = exp1_wide.df, REML = FALSE)

model_2 <- lmer(avg ~ experiment + response_order + (1 | scenario) + (1 | participant),
                data = exp1_wide.df, REML = FALSE)

model_3 <- lmer(avg ~ experiment * response_order + (1 | scenario) + (1 | participant),
                data = exp1_wide.df, REML = FALSE)

anova(model_0, model_1, model_2, model_3)

# Model 2: main effects only
cat("\n--- Model 2: experiment + response_order ---\n")
coef(summary(model_2))

# Model 3: interaction
cat("\n--- Model 3: experiment × response_order ---\n")
```

```{r option-values-contrasts, message=FALSE, warning=FALSE}
emm_options(pbkrtest.limit = 50000, lmerTest.limit = 50000)

# Estimated marginal means for each experiment × response_order cell
emm <- emmeans(model_3, ~ experiment * response_order)

# LLM vs. Human at each generation position
contrast(emm, method = "revpairwise", by = "response_order")

# Change across generation positions within each condition (vs. position 1)
contrast(emm, method = "trt.vs.ctrl", ref = 1, by = "experiment")
```

### Descriptive Statistics: Value of Generated Options

```{r desc-options, echo=FALSE, message=FALSE, warning=FALSE}
# Overall mean and SD by experimental condition
desc_options_condition <- exp1_wide.df %>%
  group_by(Condition = experiment) %>%
  summarise(Mean = round(mean(avg, na.rm = TRUE), 2),
            SD   = round(sd(avg,   na.rm = TRUE), 2),
            .groups = "drop")

knitr::kable(desc_options_condition,
             caption = "Mean composite value of generated options by condition")

# Mean and SD by condition × generation position
desc_options_order <- exp1_wide.df %>%
  group_by(Condition = experiment, `Generation position` = response_order) %>%
  summarise(Mean = round(mean(avg, na.rm = TRUE), 2),
            SD   = round(sd(avg,   na.rm = TRUE), 2),
            .groups = "drop")

knitr::kable(desc_options_order,
             caption = "Mean composite value of generated options by condition and generation position")
```


## Value of Actual Action

We tested whether participants' ratings of their own actual action differed
between conditions.

```{r actual-action, message=FALSE, warning=FALSE}
model_act <- lmer(avg ~ experiment + (1 | scenario) + (1 | participant),
                  data = exp1_wide_act.df, REML = FALSE)

anova(model_act)
coef(summary(model_act))
```

### Descriptive Statistics: Value of Actual Action

```{r desc-action, echo=FALSE, message=FALSE, warning=FALSE}
desc_action <- exp1_wide_act.df %>%
  group_by(Condition = experiment) %>%
  summarise(Mean = round(mean(avg, na.rm = TRUE), 2),
            SD   = round(sd(avg,   na.rm = TRUE), 2),
            .groups = "drop")

knitr::kable(desc_action,
             caption = "Mean composite value of actual action by condition")
```


## Effect of Experimental Condition and Sample Sum on Blame Ratings

We examined whether blame ratings were predicted by experimental condition
(LLM vs. Human), the sample sum, or both. All models included scenario and
participant as crossed random intercepts. Four rows with missing sample sums
(due to a missing actual action rating for one scenario) were excluded, leaving
a consistent dataset across all model comparisons.

```{r blame-models, message=FALSE, warning=FALSE}
# Null model
model_null <- lmer(blame ~ 1 + (1 | scenario) + (1 | participant),
                   data = exp1_blame.df, REML = FALSE)

# Experiment only
model_exp <- lmer(blame ~ experiment + (1 | scenario) + (1 | participant),
                  data = exp1_blame.df, REML = FALSE)

# Sample sum only
model_sample <- lmer(blame ~ sampleSum + (1 | scenario) + (1 | participant),
                     data = exp1_blame.df, REML = FALSE)

# Experiment + sample sum (full model)
full_model <- lmer(blame ~ experiment + sampleSum + (1 | scenario) + (1 | participant),
                   data = exp1_blame.df, REML = FALSE)

# Model comparison: does experiment condition predict blame?
cat("--- Null vs. experiment ---\n")
anova(model_null, model_exp)
coef(summary(model_exp))

# Model comparison: does sample sum add explanatory power over experiment alone?
cat("\n--- Experiment vs. experiment + sample sum ---\n")
anova(model_exp, full_model)
coef(summary(full_model))
```

### Descriptive Statistics: Blame Ratings

```{r desc-blame, echo=FALSE, message=FALSE, warning=FALSE}
desc_blame <- exp1_blame.df %>%
  group_by(Condition = experiment) %>%
  summarise(Mean = round(mean(blame, na.rm = TRUE), 2),
            SD   = round(sd(blame,   na.rm = TRUE), 2),
            .groups = "drop")

knitr::kable(desc_blame,
             caption = "Mean blame rating by condition")
```


# Figures

## Blame Ratings by Condition

```{r figure-blame, echo=FALSE, message=FALSE, warning=FALSE}
FigB <- exp1.df %>%
  mutate(blame = as.numeric(blame)) %>%
  ggplot(aes(x = factor(experiment), fill = factor(experiment), y = blame)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge",
               colour = "black", alpha = 0.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar",
               position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2),
              alpha = 0.08, colour = "black") +
  scale_fill_manual(values = c("#7DC0A6", "#B0D667"),
                    labels = c("Human", "LLM")) +
  labs(x = NULL, y = "Blame Rating", title = "Blame Judgment") +
  theme_bw() +
  theme(
    plot.title      = element_text(size = 16, hjust = 0.5),
    plot.background = element_blank(),
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text      = element_text(color = "black", size = 14),
    axis.text.y     = element_text(size = rel(1.4)),
    axis.title      = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x     = element_text(size = 16),
    axis.ticks      = element_blank(),
    legend.text     = element_text(size = rel(1.5)),
    legend.title    = element_text(size = rel(1.5))
  ) +
  guides(fill = "none")

plot(FigB)
ggsave(FigB, file = "../figures/figB.jpg", width = 4, height = 6, dpi = 300)
```

## Value of Generated Options by Generation Number

```{r figure-options, echo=FALSE, fig.height=5.25, fig.width=7, message=FALSE, warning=FALSE}
fig2 <- exp1_long.df %>%
  filter(response_category != "counterfactual",
         response_order != "act") %>%
  mutate(
    response_category = factor(response_category,
                                levels = c("probability", "morality", "normality")),
    response       = as.numeric(response),
    response_order = factor(response_order,
                            levels = c("1", "2", "3", "4", "5"))
  ) %>%
  ggplot(aes(x = response_order, y = response, fill = experiment)) +
  geom_boxplot(position = "dodge", alpha = 0.6, outlier.alpha = 0) +
  geom_smooth(
    data = . %>% filter(response_order %in% c("1", "2", "3", "4", "5")),
    aes(y = response, x = as.numeric(as.character(response_order)),
        color = experiment),
    method = "lm",
    position = position_dodge(width = 0.75),
    inherit.aes = FALSE
  ) +
  scale_fill_manual(values = c("#7DC0A6", "#B0D667"),
                    labels = c("Human", "LLM")) +
  scale_color_manual(values = c("#7DC0A6", "#B0D667"),
                     labels = c("Human", "LLM")) +
  labs(x = "Generation number", y = "Value of option generated",
       fill = "Condition:", color = "Condition:") +
  theme_bw() +
  theme(
    plot.background  = element_blank(),
    legend.position  = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text       = element_text(color = "black", size = 14),
    axis.text.y      = element_text(size = rel(1.4)),
    axis.title       = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x      = element_text(size = rel(1.5)),
    axis.ticks       = element_blank(),
    legend.text      = element_text(size = rel(1.5)),
    legend.title     = element_text(size = rel(1.5))
  ) +
  facet_wrap(~ response_category)

fig2
ggsave(fig2, file = "../figures/fig2.jpg", width = 11, height = 6, dpi = 300)
```

## Value of Chosen Action by Condition

```{r figure-action, echo=FALSE, message=FALSE, warning=FALSE}
FigA <- exp1_wide_act.df %>%
  ggplot(aes(x = experiment, fill = experiment, y = avg)) +
  geom_boxplot(width = 0.55, alpha = 0.5, colour = "black",
               outlier.shape = NA) +
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2),
              alpha = 0.08, colour = "black") +
  stat_summary(fun = mean, geom = "point", size = 3, colour = "black") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar",
               width = 0.15, colour = "black") +
  scale_fill_manual(values = c("#7DC0A6", "#B0D667"),
                    labels = c("Human", "LLM")) +
  labs(title = "Value of Chosen Action",
       x = NULL, y = "Average Value of Chosen Action") +
  theme_bw() +
  theme(
    plot.title       = element_text(size = 16, hjust = 0.5),
    plot.background  = element_blank(),
    legend.position  = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text       = element_text(color = "black", size = 14),
    axis.text.y      = element_text(size = rel(1.4)),
    axis.title       = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x      = element_text(size = 16),
    axis.ticks       = element_blank(),
    legend.text      = element_text(size = rel(1.5)),
    legend.title     = element_text(size = rel(1.5))
  ) +
  guides(fill = "none")

plot(FigA)
ggsave(FigA, file = "../figures/figA.jpg", width = 4, height = 6, dpi = 300)
```
