---
title: "Analyze Distances"
author: ""
date: "2026-01-13"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

```{r setup, include=FALSE} 
library(tidyverse)
library(tibble)
library(readr)
library(lmerTest)
library(nlme)
library(knitr)
library(ggrepel)
library(irr)  # Install this package once outside of the document
library(purrr)
library(janitor)
library(stringr)
library(data.table)
library(arrow)
library(emmeans)
library(forcats)
library(viridis)
library(patchwork)
library(emmeans)
library(car)
library(quanteda)
library(quanteda.textstats)
library(udpipe)

rm(list = ls()) 
knitr::opts_chunk$set(echo = TRUE, dpi = 300, fig.width = 7)  # Set echo = TRUE for troubleshooting

# options(digits = 2) # round after 2 significant digits

if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
  this_file <- rstudioapi::getActiveDocumentContext()$path
  setwd(dirname(this_file))
}
```

## Load data from analysis.iypnb
```{r}
df <- read_csv("output/original/distances_and_clusters.csv")
```


## Wrangle Data
```{r}
df <- df %>%
  rename(experimental_condition = type,
         generation_number = response_number,
         centroid_dist = p_dist_cosine,
         m_pairwise_dist = m_dist_cosine) %>% 
  mutate(participant = as.character(response_id)) %>%
  mutate(
    scenario = factor(scenario),
    generation_number = as.numeric(generation_number),
    llm = ifelse(str_detect(experimental_condition, "llm"), 1, 0)
  )

df <- df %>% filter(experimental_condition != "action")
```


# Descriptives

```{r}
df$word_count <- ntoken(df$response, remove_punct = TRUE)


df %>% group_by(experimental_condition) %>% 
  summarise(
    mean_c_dist = mean(centroid_dist, na.rm = T),
    mean_pairwise_dist = mean(m_pairwise_dist, na.rm = T),
    mean_word_count = mean(word_count, na.rm = T),
    min_word_count = min(word_count, na.rm = T),
    max_word_count = max(word_count, na.rm = T)
  )

vars <- df %>% 
  select(centroid_dist, m_pairwise_dist, llm, generation_number , word_count)

cor(vars, use = "pairwise.complete.obs")
```


# 1. MEAN PAIRWISE COSINE DISTANCE
Mean paiwise cosine distance between options a participant or LLM generated within a scenario.

## 1.1. Group-Level Descriptives
```{r}

m_dist <- ggplot(df, aes(x = experimental_condition, y = m_pairwise_dist)) +
  geom_violin(trim = FALSE, alpha = 0.6) +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.7) +  theme_classic() +
  labs(
    x = "experimental_condition",
    y = "Mean Pairwise Cosine distance within a Participant"
  )

m_dist

df %>%
  group_by(experimental_condition) %>%
  summarise(
    mean = mean(m_pairwise_dist, na.rm = TRUE),
    sd = sd(m_pairwise_dist, na.rm = TRUE),
    var = var(m_pairwise_dist, na.rm = TRUE),
    n = sum(!is.na(m_pairwise_dist)),
    .groups = "drop"
  )
```


## 1.2. Mixed-Effects Model
```{r}
m_dist_het <- lme(
  fixed = m_pairwise_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~ 1, participant = ~1),
  weights = varIdent(form = ~ 1 | experimental_condition),         # unequal residual variance by experimental_condition
  data = df,
  method = "REML"
)

summary(m_dist_het)

# Simple slopes for interaction
print(test(emtrends(m_dist_het, ~ experimental_condition, var = "generation_number")))
```

## 1.3. LR Test for variance

```{r}

m_dist_hom <- lme(
  fixed = m_pairwise_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~ 1, participant = ~1),
  data = df,
  method = "REML"
)

print(anova(m_dist_hom, m_dist_het))

```
## 1.4. LR Test for interaction

```{r}

m_add <- lme(
  m_pairwise_dist ~ experimental_condition + generation_number,
  random = list(scenario = ~1, participant = ~1),
  weights = varIdent(form = ~1 | experimental_condition),
  data = df,
  method = "ML"
)

m_int <- lme(
  m_pairwise_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~1, participant = ~1),
  weights = varIdent(form = ~1 | experimental_condition),
  data = df,
  method = "ML"
)

print(anova(m_add, m_int)) # LR test for the interaction
```


## 1.5. Model Diagnostics
```{r, fig.width=15, fig.height=5, out.width="100%"}
diag_m_dist <- data.frame(
  fitted = fitted(m_dist_het),
  resid  = resid(m_dist_het, type = "normalized")
)

p_resid_m_dist <- ggplot(diag_m_dist, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(title = "Residuals vs Fitted")

p_qq_res_m_dist <- ggplot(
  data.frame(resid = resid(m_dist_het, type = "normalized")),
  aes(sample = resid)
) +
  stat_qq(alpha = 0.6) +
  stat_qq_line(linetype = "dashed") +
  theme_classic() +
  labs(title = "Normal Q-Q (Normalized residuals)")

re_df <- ranef(m_dist_het)
re_response <- re_df$participant[, "(Intercept)"]

p_qq_re_response <- ggplot(
  data.frame(re = re_response),
  aes(sample = re)
) +
  stat_qq(alpha = 0.3) +
  stat_qq_line(linetype = "dashed") +
  theme_classic() +
  labs(title = "Normal Q-Q (Random effects: participant)")

p_resid_m_dist + p_qq_res_m_dist + p_qq_re_response +
  plot_layout(ncol = 3)
```

# 2. CENTROID DISTANCE
Cosine distance to the Centroid of the 5 options a participant or LLM generated within a scenario.

## 2.1. Group-Level Descriptives
```{r}

p_centroid <- ggplot(df, aes(x = experimental_condition, y = centroid_dist)) +
  geom_violin(trim = FALSE, alpha = 0.6) +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.7) +
  theme_classic() +
  labs(
    x = "experimental_condition",
    y = "Cosine distance to Participant Centroid"
  )

p_centroid

df %>%
  group_by(experimental_condition) %>%
  summarise(
    mean = mean(centroid_dist, na.rm = TRUE),
    sd = sd(centroid_dist, na.rm = TRUE),
    var = var(centroid_dist, na.rm = TRUE),
    n = sum(!is.na(centroid_dist)),
    .groups = "drop"
  )
```


## 2.2. Mixed-Effects Model
```{r}
p_centroid_het <- lme(
  fixed = centroid_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~ 1, participant = ~1),
  weights = varIdent(form = ~ 1 | experimental_condition),         # unequal residual variance by experimental_condition
  data = df,
  method = "REML"
)

summary(p_centroid_het)

# Simple slopes for interaction
print(test(emtrends(p_centroid_het, ~ experimental_condition, var = "generation_number")))
```

## 2.3. LR Test for variance

```{r}
p_centroid_het <- lme(
  fixed = centroid_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~ 1, participant = ~1),
  weights = varIdent(form = ~ 1 | experimental_condition),         # unequal residual variance by experimental_condition
  data = df,
  method = "REML"
)

p_centroid_hom <- lme(
  fixed = centroid_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~ 1, participant = ~1),
  data = df,
  method = "REML"
)

print(anova(p_centroid_hom, p_centroid_het))
```
## 2.4. LR Test for interaction

```{r}
p_add <- lme(
  centroid_dist ~ experimental_condition + generation_number,
  random = list(scenario = ~1, participant = ~1),
  weights = varIdent(form = ~1 | experimental_condition),
  data = df,
  method = "ML"
)

p_int <- lme(
  centroid_dist ~ experimental_condition * generation_number,
  random = list(scenario = ~1, participant = ~1),
  weights = varIdent(form = ~1 | experimental_condition),
  data = df,
  method = "ML"
)

print(anova(p_add, p_int))   # LR test for the interaction
```


## 2.5. Model Diagnostics
```{r, fig.width=15, fig.height=5, out.width="100%"}
diag_centroid <- data.frame(
  fitted = fitted(p_centroid_het),
  resid  = resid(p_centroid_het, type = "normalized")
)

p_resid_centroid <- ggplot(diag_centroid, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  labs(title = "Residuals vs Fitted")

p_qq_res_centroid <- ggplot(
  data.frame(resid = resid(p_centroid_het, type = "normalized")),
  aes(sample = resid)
) +
  stat_qq(alpha = 0.6) +
  stat_qq_line(linetype = "dashed") +
  theme_classic() +
  labs(title = "Normal Q-Q (Normalized residuals)")

re_df <- ranef(p_centroid_het)
re_response <- re_df$participant[, "(Intercept)"]

p_qq_re_response <- ggplot(
  data.frame(re = re_response),
  aes(sample = re)
) +
  stat_qq(alpha = 0.3) +
  stat_qq_line(linetype = "dashed") +
  theme_classic() +
  labs(title = "Normal Q-Q (Random effects: participant)")

p_resid_centroid + p_qq_res_centroid + p_qq_re_response +
  plot_layout(ncol = 3)
```

# ROBUSTNESS CHECKS

## WORD COUNT CONTROL
Although including word count as a control preserves statistical significance for mean-pairwise-distance, the limited common support across conditions means the adjustment relies on extrapolation outside the overlap region rather than on within-range comparison. We therefore exclude word count as a covariate.

```{r}
# Check for support
ggplot(df, aes(x = word_count, color = experimental_condition, fill = experimental_condition)) +
  geom_density(alpha = 0.2) +
  labs(
    x = "Wordcount",
    y = "Density",
    title = "Density of Wordcount by Experimental Condition"
  ) +
  theme_minimal()
```

```{r}
c_wc <- lme(
  fixed = centroid_dist ~ experimental_condition * generation_number + word_count,
  random = list(scenario = ~ 1, participant = ~1),
  weights = varIdent(form = ~ 1 | experimental_condition),         # unequal residual variance by experimental_condition
  data = df,
  method = "REML"
)

vif(c_wc)


pd_wc <- lme(
  fixed = m_pairwise_dist ~ experimental_condition * generation_number + word_count,
  random = list(scenario = ~ 1, participant = ~1),
  weights = varIdent(form = ~ 1 | experimental_condition),         # unequal residual variance by experimental_condition
  data = df,
  method = "REML"
)

vif(pd_wc)

summary(c_wc)
summary(pd_wc)
```






