----
title: "LLM & Human Possibilities"
date: "November 2025"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(tibble)
library(readr)
library(lme4)
library(knitr)
library(ggrepel)
library(irr)  # Install this package once outside of the document
library(purrr)
library(janitor)
library(stringr)
library(data.table)
library(arrow)

rm(list = ls()) 

knitr::opts_chunk$set(echo = TRUE, dpi = 300, fig.width = 7)  # Set echo = TRUE for troubleshooting
```


```{r}

hum <- fread("data/main/human.csv")

llm1 <- fread("data/main/llm.csv")
llm1[, `icecream2` := NULL]

llm2 <- fread("data/main/llm2.csv")

# Base R
llm <- rbind(llm1, llm2)


# hum <- fread("data/pilot_1/pilot_human.csv")
# llm <- fread("data/pilot_1/pilot_llm.csv")

```



# Read and merge data from Human and LLM Condition
```{r}

llm.df <- llm %>% 
   clean_names() %>%       # fixes duplicates & makes snake_case
   select(-matches("_Response")) %>% 
  mutate(experiment = "LLM") %>% 
  slice(-c(1:2))

hum.df <- hum %>% 
  clean_names() %>% 
   select(-matches("_fr_")) %>% 
   mutate(experiment = "Human") %>% 
   slice(-c(1:2)) 



main.df <- bind_rows(llm.df, hum.df) %>% 
     filter(progress == 100,
             distribution_channel != "preview") %>% 
   #turn empty string into NA
   mutate(across(everything(), ~ na_if(., "")))

```

# Filter for bots / exclusion criteria

```{r}
main.df <- subset(
  main.df,
  is.na(compromised) |
    !(
      (compromised == "Yes") |
      (!is.na(q_recaptcha_score) & q_recaptcha_score <= 0.5) |
      (!is.na(icecream) & icecream == "Salt and Pepper")
    )
)


```

# Demographics

```{r}
desc1.df<-main.df %>% 
  select(duration_in_seconds, ethnicity, ethnicity_10_text, gender)%>% 
    mutate(duration_in_seconds=as.numeric(duration_in_seconds)) %>% 
    summarise(n=n(),
             female=sum(gender=="Female"),
             male=sum(gender=="Male"),
             non_binary=sum(gender=="Non-Binary"),
             undisclosed=sum(gender=="Prefer not to say"),
             other=sum(gender=="Other"),
             white=sum(ethnicity=="Caucasian/White"),
             black=sum(ethnicity=="Black/African"),
             latino=sum(ethnicity=="Hispanic/Latinx"),
             native=sum(ethnicity=="Alaskan or American Indian"),
             asian=sum(ethnicity=="Asian"),
             east=sum(ethnicity=="Middle Eastern or Northern African"),
             multi=sum(ethnicity=="Multiethnic"),
             e_undisclosed=sum(ethnicity=="Prefer not to disclose"),
             mean_time=mean(duration_in_seconds/60),
             sd_time=sd(duration_in_seconds/60)) 


desc_age.df<-main.df %>% 
mutate(age= as.numeric(age)) %>% 
  select(age)%>% 
  filter(age!="") %>% 
  filter(age<100) %>% 
        summarise(
              mean_age = mean(age, na.rm = TRUE),
              sd_age   = sd(age,  na.rm = TRUE))


```


## Data Wrangling
#Create Basic Wide Dataframe with all ratings

```{r}
exp1.df<-main.df %>% 
  mutate(participant = 1:n()) %>% 
  select(x1_s1_t_first_click:x117_s9_cf5_6,
         x120_s5_t_first_click:x223_s5_cf5_6,
         participant,
         experiment,
         condition)%>%
    select(-contains("last_click"), -contains("click_count")) %>% 
  gather(category, response, -participant,-experiment, -condition) %>% 
  filter(response != "") %>% 
  mutate(exp_condition = case_when(
    str_detect(condition, "1") ~ "judgment last",
    str_detect(condition, "2") ~ "judgment first")) %>% 
    mutate(scenario = case_when(
    str_detect(category, "s1_") ~ "scenario 1",
    str_detect(category, "s2_") ~ "scenario 2",
    str_detect(category, "s3_") ~ "scenario 3",
    str_detect(category, "s4_") ~ "scenario 4",
    str_detect(category, "s5_") ~ "scenario 5",
    str_detect(category, "s6_") ~ "scenario 6",
    str_detect(category, "s7_") ~ "scenario 7",
    str_detect(category, "s8_") ~ "scenario 8",
    str_detect(category, "s9_") ~ "scenario 9")) %>% 
  mutate(responsetype = case_when(
    str_detect(category, "a1_4") ~ "prob_resp_1",
    str_detect(category, "a1_5") ~ "moral_resp_1",
    str_detect(category, "a1_6")  ~ "normal_resp_1",
    str_detect(category, "a2_4") ~ "prob_resp_2",
    str_detect(category, "a2_5") ~ "moral_resp_2",
    str_detect(category, "a2_6")  ~ "normal_resp_2",
    str_detect(category, "a3_4") ~ "prob_resp_3",
    str_detect(category, "a3_5") ~ "moral_resp_3",
    str_detect(category, "a3_6")  ~ "normal_resp_3",
    str_detect(category, "a4_4") ~ "prob_resp_4",
    str_detect(category, "a4_5") ~ "moral_resp_4",
    str_detect(category, "a4_6")  ~ "normal_resp_4",
    str_detect(category, "a5_4") ~ "prob_resp_5",
    str_detect(category, "a5_5") ~ "moral_resp_5",
    str_detect(category, "a5_6")  ~ "normal_resp_5",
    str_detect(category, "ar_4") ~ "prob_resp_act",
    str_detect(category, "ar_5") ~ "moral_resp_act",
    str_detect(category, "ar_6")  ~ "normal_resp_act",
    str_detect(category, "b_")  ~ "blame",
    str_detect(category, "cf1") ~ "cf_1",
    str_detect(category, "cf2") ~ "cf_2",
    str_detect(category, "cf3") ~ "cf_3",
    str_detect(category, "cf4") ~ "cf_4",
    str_detect(category, "cf5") ~ "cf_5",
    str_detect(category, "first_click") ~ "first_click",
    str_detect(category, "page_submit") ~ "page_submit"
  )) %>% 
      select(-condition, -category) %>% 
    pivot_wider(names_from = responsetype,
              values_from = response) 


  
participant_counts <- exp1.df %>%
  group_by(experiment, scenario) %>%
  summarise(count = n()) %>%
  ungroup()

participant_counts2 <- exp1.df %>%
  group_by(experiment) %>%
  summarise(count = n()) %>%
  ungroup()


```

#Delete columns in which data were missing due to a coding error


```{r}
library(dplyr)

exp1.df <- exp1.df %>% 
  # 1. Drop rows where ALL three *_resp_act columns are NULL
  filter(
    !(sapply(prob_resp_act,   is.null) &
      sapply(moral_resp_act,  is.null) &
      sapply(normal_resp_act, is.null))
  ) %>% 
  # 2. Keep only rows where blame has exactly one value
  #    (this removes NULLs and double entries like c("0", "0"))
  filter(sapply(blame, length) == 1)


exp_out.df <- exp1.df %>% 
  filter(sapply(blame, length) != 1)


```


## Create a variety of Long and Wide Format Dataframes

```{r}

#All Data Long Format
exp1_long.df = exp1.df %>% 
    gather(responsetype, response, -scenario, -participant, -exp_condition, -experiment, -first_click, -page_submit, - blame) %>%
 mutate(response_order = case_when(
    str_detect(responsetype, "_1") ~ "1",
    str_detect(responsetype, "_2") ~ "2",
    str_detect(responsetype, "_3") ~ "3",
    str_detect(responsetype, "_4") ~ "4",
    str_detect(responsetype, "_5") ~ "5",
    str_detect(responsetype, "_act") ~ "act",
    )) %>% 
  mutate(response_category = case_when(
    str_detect(responsetype, "prob_") ~ "probability",
    str_detect(responsetype, "moral_") ~ "morality",
    str_detect(responsetype, "normal_") ~ "normality",
    str_detect(responsetype, "cf_") ~ "counterfactual")) %>% 
    select(-responsetype) 

#All Data Wide Format
exp1_wide.df = exp1_long.df %>% 
  pivot_wider(names_from = response_category,
              values_from = response) %>% 
  mutate(across(c(probability, morality, normality), as.numeric)) %>% 
    mutate(avg=(normality+probability+morality)/3)


#Just Actual Actions Data with averaged rating in Wide Format
exp1_long_avg.df <- exp1_wide.df %>%
  pivot_longer(
    cols = c(probability, morality, normality, avg),  # Columns to pivot
    names_to = "response_category", 
    values_to = "response"
  ) %>% 
    filter(response_order!= "act") %>% 
  mutate(response=as.numeric(response))


#Mean ratings of actual action
exp1_long_act.df <- exp1_wide.df %>%
  pivot_longer(
    cols = c(probability, morality, normality, avg),  # Columns to pivot
    names_to = "response_category", 
    values_to = "response"
  ) %>% 
    filter(response_order== "act") %>% 
  mutate(response=as.numeric(response)) %>% 
    group_by(scenario, response_category, experiment) %>%
      summarise(mean = mean(response, na.rm = TRUE), .groups = "drop")


#Actual action ratings
exp1_long_act2.df <- exp1_wide.df %>%
  pivot_longer(
    cols = c(probability, morality, normality, avg),  # Columns to pivot
    names_to = "response_category", 
    values_to = "response"
  ) %>% 
    filter(response_order== "act") %>% 
  mutate(response=as.numeric(response))

```

# Calculate  Sample Sum and Sample Sum 2 

```{r}
library(dplyr)
withinData <- exp1_long_avg.df %>% 
  mutate(sampleSum = NA, sampleSum2 = NA)


for (subj in unique(withinData$participant)) {  ## for each participant
  d <- withinData %>% filter(participant == subj)
  
  ## Loop through each experiment and scenario combination
  for (e in unique(d$experiment)) {
    for (c in unique(d$scenario)) {
      
      # Sample the individual ratings from exp1_long_avg for the "avg" category
      pgSamp <- exp1_long_avg.df %>%
        filter(participant == subj, scenario == c, experiment == e, response_category == "avg") %>%
        pull(response)
      
      # Get the individual action rating for the participant for each scenario and experiment
      a_val <- exp1_long_act2.df %>%
        filter(participant == subj, scenario == c, experiment == e, response_category == "avg") %>%
        pull(response)  
      
      #Sample Sum: Calculate the sum of values of actions that were rated higher than the individual rating of the actual action
      withinData$sampleSum[withinData$participant == subj & withinData$scenario == c & withinData$experiment == e] <- sum(pgSamp[a_val<pgSamp])
      
      
    #Sample Sum 2: Calculate the sum of values of actions that were rated higher than the individual rating of the actual action, but subtract the value of the actual action
      withinData$sampleSum2[withinData$participant == subj & withinData$scenario == c & withinData$experiment == e] <- sum(pgSamp[pgSamp > a_val] - a_val)


    }
  }
}

# Optionally print or view the updated data
print(withinData)

```


#Create New Dataframe for Analysis

```{r}
exp1_model.df<-withinData %>%  
   filter(response_order==1 & response_category=="avg") %>% 
  mutate(blame=as.numeric(blame))
```


# Create Wide Dataframe

```{r}
#All Data Wide Format
exp1_wide.df = exp1_long.df %>% 
  pivot_wider(names_from = response_category,
              values_from = response) %>% 
  mutate(across(c(probability, morality, normality), as.numeric)) %>% 
    mutate(avg=(normality+probability+morality)/3) %>% 
      filter(response_order!= "act") %>% 
  mutate(
    experiment = relevel(factor(experiment), ref = "Human")  # change "Human" to your baseline
  ) %>% 
    mutate(
    response_order = ordered(as.integer(as.character(response_order)),
                             levels = 1:5)
  )

```



## Values of options generated
```{r}

library(lme4)
library(lmerTest)
library(emmeans)

# Fit LMER models to predict avg rating based on experiment and response order
#### Three Models
model_0 <- lmer(avg ~ + (1 | scenario) + (1 | participant), 
                   data = exp1_wide.df, REML = FALSE)

model_1 <- lmer(avg ~ experiment + (1 | scenario) + (1 | participant), 
                   data = exp1_wide.df, REML = FALSE)

model_2 <- lmer(avg ~ experiment + response_order + (1 | scenario) + (1 | participant), 
                   data = exp1_wide.df, REML = FALSE)

model_3 <- lmer(avg ~ experiment * response_order + (1 | scenario) + (1 | participant), 
                   data = exp1_wide.df, REML = FALSE)

anova(model_0, model_1, model_2, model_3)

### Model 1 stats
fixef(model_1)              # named vector of fixed-effect estimates ("betas")
coef(summary(model_1))      # estimates + SE + t value
confint(model_1, method="Wald")  # CIs (fast)


### Model 2 stats
fixef(model_2)              # named vector of fixed-effect estimates ("betas")
coef(summary(model_2))      # estimates + SE + t value
confint(model_2, method="Wald")  # CIs (fast)




emm_options(pbkrtest.limit = 50000, lmerTest.limit = 50000)
emmeans::emm_options(pbkrtest.limit = 50000, lmerTest.limit = 50000)


# Estimated means for each cell
emm <- emmeans(model_3, ~ experiment * response_order)
exp1_wide.df$response_order <- ordered(exp1_wide.df$response_order, levels = 1:5)
contrasts(exp1_wide.df$response_order) <- contr.poly(5)


# LLM vs Human (or whatever reference) at each response_order
contrast(emm, method = "revpairwise", by = "response_order")  # or "pairwise"

# response_order differences within each experiment
contrast(emm, method = "trt.vs.ctrl", ref = 1, by = "experiment")

str(exp1_wide.df$experiment)
str(exp1_wide.df$response_order)
contrasts(exp1_wide.df$experiment)
contrasts(exp1_wide.df$response_order)


```

## Value of actual action

```{r}

#All Data Wide Format singling out only the actual action

exp1_wide_act.df = exp1_long.df %>% 
        filter(response_order== "act") %>% 
  pivot_wider(names_from = response_category,
              values_from = response) %>% 
  mutate(across(c(probability, morality, normality), as.numeric)) %>% 
    mutate(avg=(normality+probability+morality)/3) %>%   mutate(
    experiment = relevel(factor(experiment), ref = "Human")  # change "Human" to your baseline
  ) 

# Predictig the avg rating of the actual action based on experimental conditin
model_act <- lmer(avg ~ + experiment*exp_condition + (1 | scenario) + (1 | participant), 
                   data = exp1_wide_act.df, REML = FALSE)

### Model "act" stats
anova(model_act)
fixef(model_act)              # named vector of fixed-effect estimates ("betas")
coef(summary(model_act))      # estimates + SE + t value
confint(model_0, method="Wald")  # CIs (fast)

```


##The Effect of experimental condition and option sum on blame ratings

```{r}


# Full model (both predictors)
full_model <- lmer(blame ~ experiment + sampleSum2 + (1 | scenario) + (1 | participant), 
                   data = exp1_model.df, REML = FALSE)

# Reduced model with only 'experiment'
model_exp <- lmer(blame ~ experiment + (1 | scenario) + (1 | participant), 
                  data = exp1_model.df, REML = FALSE)

# Reduced model with only 'sampleDistance'
model_sample <- lmer(blame ~ sampleSum2 + (1 | scenario) + (1 | participant), 
                     data = exp1_model.df, REML = FALSE)

# Null
model_null <- lmer(blame ~ 1 + (1 | scenario) + (1 | participant), 
                     data = exp1_model.df, REML = FALSE)

# Compare null model vs. experiment-only model
anova(model_null, model_exp)
fixef(model_exp)              # named vector of fixed-effect estimates ("betas")
coef(summary(model_exp))      # estimates + SE + t value
confint(model_exp, method="Wald")

# Compare experiment-only model vs. full model
anova(model_exp, full_model)
fixef(full_model)              # named vector of fixed-effect estimates ("betas")
coef(summary(full_model))      # estimates + SE + t value
confint(full_model, method="Wald")




```


##### Figures

```{r}
#Set theme

myTheme <- theme(
  axis.title.x = element_blank(), 
  axis.title.y = element_text(color = "black", size = 16, vjust = 0.9), 
  axis.text.x = element_text(color = "black", size = 16),
  axis.text.y = element_text(color = "black", size = 16), 
  strip.text.x = element_text(color = "black", size = 16), # Facet title font
  legend.text = element_text(color = "black", size = 16),
  legend.title = element_text(color = "black", size = 16),
  legend.position = "top",
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  strip.background = element_rect(fill = "white") # White background for facet titles
)

```


#Figure Blame Ratings

```{r}
FigB <- exp1.df %>% 
  mutate(blame = as.numeric(blame)) %>%
  #filter(scenario=="scenario 3") %>% 
  ggplot(aes(x=factor(experiment), fill=factor(experiment), y=blame)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge", colour = "black", alpha=0.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2), alpha = 0.08, colour="black") +
  scale_fill_manual(
    values = c("#7DC0A6", "#B0D667"), # Set custom fill colors
    labels = c("Human", "LLM") # Customize legend labels
  )+labs(x=NULL, y="Blame Rating",title = "Blame Judgment") +
  #facet_wrap(~scenario)+
      theme_bw()+
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.background = element_blank(),
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(color = "black", size = 14), # Apply to all strip text (facet titles)
    axis.text.y = element_text(size = rel(1.4)),
    axis.title = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x = element_text(size = 16),
    axis.ticks = element_blank(),
    legend.text = element_text(size = rel(1.5)),
    legend.title = element_text(size = rel(1.5))
  ) +
  guides(fill = "none")


plot(FigB)

ggsave(FigB, file = "figB.jpg", width = 4, height = 6, dpi = 300)

```

```{r}
FigB <- exp1.df %>% 
  mutate(blame = as.numeric(blame)) %>%
  filter(scenario == "scenario 3") %>% 
  ggplot(aes(x = factor(experiment), y = blame, fill = factor(experiment))) +
  
  # distribution
  geom_violin(trim = FALSE, alpha = 0.5, colour = "black") +
  
  # raw points
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2),
              alpha = 0.08, colour = "black") +
  
  # mean (point) + optional CI (bootstrapped)
  stat_summary(fun = mean, geom = "point",
               size = 3, colour = "black") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar",
               width = 0.15, colour = "black") +
  
  scale_fill_manual(
    values = c("#7DC0A6", "#B0D667"),
    labels = c("Human", "LLM")
  ) +
  labs(y = "Blame Rating") +
  theme_bw() +
  myTheme +
  guides(fill = "none")

plot(FigB)

ggsave(FigB, file = "figB.jpg", width = 10, height = 9, dpi = 300)

```
```{r}
FigB <- exp1.df %>% 
  mutate(blame = as.numeric(blame)) %>%
  #filter(scenario == "scenario 3") %>% 
  ggplot(aes(x = factor(experiment), y = blame, fill = factor(experiment))) +
  
  # boxplot
  geom_boxplot(width = 0.55, alpha = 0.5, colour = "black",
               outlier.shape = NA) +
  
  # raw points
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2),
              alpha = 0.08, colour = "black") +
  
  # mean (point) + optional bootstrapped CI
  stat_summary(fun = mean, geom = "point",
               size = 3, colour = "black") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar",
               width = 0.15, colour = "black") +
  
  scale_fill_manual(
    values = c("#7DC0A6", "#B0D667"),
    labels = c("Human", "LLM")
  ) +
  labs(y = "Blame Rating") +
  theme_bw() +
  myTheme +
  guides(fill = "none")

plot(FigB)

ggsave(FigB, file = "figB.jpg", width = 10, height = 9, dpi = 300)

```
# Nicer figure with Boxplots of all ratings by action generation number + actual action


```{r fig1, echo=F, fig.height=5.25, fig.width=7, message=FALSE, warning=FALSE}

 fig2 <- exp1_long.df %>% 
  #filter(scenario=="scenario 3") %>% 
  filter(response_category != "counterfactual") %>% 
  filter(response_order!= "act") %>% 
  mutate(response_order = ifelse(response_order == "act", "action", response_order)) %>% 
  mutate(
    response_category = factor(response_category, levels = c("probability", "morality", "normality")), # Reorder levels
    response = as.numeric(response),
    response_order = factor(response_order, levels = c("1", "2", "3", "4", "5", "action")) # Ensure "act" is a level
  ) %>%
  ggplot(aes(x = response_order, y = response, fill = experiment)) +
  geom_boxplot(position = "dodge", alpha = 0.6, outlier.alpha = 0) +
    geom_smooth(
    data = . %>% filter(response_order %in% c("1", "2", "3", "4", "5")), # Restrict only for smoothing
    aes(y = response, x = as.numeric(as.character(response_order)), color = experiment),
    method = "lm",
    position = position_dodge(width = 0.75),
    inherit.aes = FALSE
  )+
  #geom_point(aes(color = response_category), position = position_jitterdodge(jitter.width = 0.35), alpha = 0.05) +
  scale_fill_manual(
     values = c("#7DC0A6", "#B0D667"), # Set custom fill colors
    labels = c("Human", "LLM") # Customize legend labels
  ) +
  scale_color_manual(
     values = c("#7DC0A6", "#B0D667"), # Match color of smoothed lines to boxplot fill
    labels = c("Human", "LLM")
  ) +
  labs(
    x = "Generation number", 
    y = "Value of option generated", 
    fill = "Rating:", 
    color = "Rating:"
  ) +
  theme_bw() +
  theme(
    plot.background = element_blank(),
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(color = "black", size = 14), # Apply to all strip text (facet titles)
    axis.text.y = element_text(size = rel(1.4)),
    axis.title = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x = element_text(size = rel(1.5)),
    axis.ticks = element_blank(),
    legend.text = element_text(size = rel(1.5)),
    legend.title = element_text(size = rel(1.5))
  ) +
  facet_wrap(~ response_category)

 fig2
ggsave(fig2, file = "fig2.jpg", width = 11, height = 6, dpi = 300)

```
#Figure Action Valuation Ratings

```{r}
FigA <- exp1_wide_act.df %>% 
  #filter(scenario=="scenario 3") %>% 
  ggplot(aes(x=experiment, fill=experiment, y=avg)) +
  # boxplot
  geom_boxplot(width = 0.55, alpha = 0.5, colour = "black",
               outlier.shape = NA) +
  
  # raw points
  geom_jitter(position = position_jitter(width = 0.15, height = 0.2),
              alpha = 0.08, colour = "black") +
  
  # mean (point) + optional bootstrapped CI
  stat_summary(fun = mean, geom = "point",
               size = 3, colour = "black") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar",
               width = 0.15, colour = "black") +
  scale_fill_manual(
    values = c("#7DC0A6", "#B0D667"), # Set custom fill colors
    labels = c("Human", "LLM") # Customize legend labels
  )+labs(
    title = "Value of Chosen Action",
    x=NULL, y="Average Value of Chosen Action") +
  #facet_wrap(~scenario)+
      theme_bw()+
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.background = element_blank(),
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(color = "black", size = 14), # Apply to all strip text (facet titles)
    axis.text.y = element_text(size = rel(1.4)),
    axis.title = element_text(size = rel(1.5), vjust = 0.9),
    axis.text.x = element_text(size = 16),
    axis.ticks = element_blank(),
    legend.text = element_text(size = rel(1.5)),
    legend.title = element_text(size = rel(1.5))
  ) +
  guides(fill = "none")


plot(FigA)

ggsave(FigA, file = "figA.jpg", width = 4, height = 6, dpi = 300)

```


```{r}
library(ggeffects)

pred <- ggpredict(full_model, terms = c("sampleSum2 [all]", "experiment"))

plot(pred) +
  theme_bw() +
  labs(x = "SampleSum2", y = "Predicted blame")

```



